Management induced changes of soil organic carbon on global croplands

### 2020-08-14 SOCbudgetPaper/results.Rmd
update written part to first official version (woohoo)

```{r caption_SOCmaps, echo=FALSE}
caption <- "(a) ... , (b) ... , (c) ... , (d) ... ."
```

```{r SOCmaps, out.width = "18cm", fig.cap = caption}
# All defaults
knitr::include_graphics("../ResultNotebooks/Output/Images/4panelfigure.png")
```

@@

```{r table, echo = FALSE}
table <- readRDS("../ResultNotebooks/Output/SFC_climatezone.rds")
knitr::kable(table$naturalstate_table, "latex", digit=2, caption="SCF compared to potential natural state")
```

```{r table2, echo = FALSE}
table <- readRDS("../ResultNotebooks/Output/SFC_comparison.rds")
knitr::kable(table$comparison_table, "latex", digit=2, caption="SCF compared to IPCC Tier 1")
```

## global agricultrual carbon flows and stocks

>>>>

```{r caption_SOCmaps, echo=FALSE}
caption_SOCmaps <- "(a): Distribution of total global SOC stocks on cropland shows high carbon stocks in high yielding areas. (b): The SOC debt is decreasing over time, meaning net SOC gains on global croplands over the last decades (despite ongoing cropland expansion). (c)+(d): Absolute (c) and relative (d) SOC stocks compared to a potential natural state showing different hot spots of SOC dynamics. Whereas the absolute losses might be in temperate dry regions, relative losses are more prominent in tropical moist areas."
```

```{r SOCmaps, out.width = "18cm", fig.cap = caption_SOCmaps, echo=FALSE, fig.pos="H"}
# All defaults
knitr::include_graphics("../ResultNotebooks/Output/Images/4panelfigure.png")
```

## global agricultural carbon flows and stocks

```{r caption_FlowFig, echo=FALSE}
caption_FlowFig <- "Global carbon flows (small numbers) and stocks (bold numbers) within the agricultural system for the year 2010 (in MtC): Most important carbon sources on cropland are crop residues. Note the two numbers on carbon inputs to soil denote carbon applied to the field and carbon entering the soil (difference is decomposted before official counting as soil)."
```

```{r FlowFig, out.width = "16cm", fig.cap = caption_FlowFig, echo=FALSE, fig.pos="H"}
# All defaults
knitr::include_graphics("../ResultNotebooks/Output/Images/OuFlowFig.png")
```

```{r caption_SCFtable, echo=FALSE}
caption_SCFtable <- "$F^{SOC}$ in comparison to IPCC Tier 1 default factors: Stock change factors are in good agreement with the default values of the IPCC in general. For the tropical regions the assumptions changed notablly from the guidelines in 2006 to the update in 2019. leaving our results in very good agreement with the old default assumptions. Default assumption are given under the assumption of medium input systems, which, considering the yield gap in mainly developing regions in the tropics, might be an overestimation and decrease $F^{SOC}$ by additional 5-8 percent. Also: modelled $F^{SOC}$ have increased for all climates over time ."
```

```{r SCFtable, out.width = "16cm", fig.cap = caption_SCFtable, echo=FALSE, fig.pos="H"}
# All defaults
knitr::include_graphics("../ResultNotebooks/Output/Images/TableSCF_comparison.png")
```

<!-- ```{r table2, echo = FALSE}
# table <- readRDS("../ResultNotebooks/Output/SFC_comparison.rds")
# knitr::kable(table$comparison_table, "latex", digit=2, 
#              caption="$F^{SOC}$ in comparison to IPCC Tier 1 default factors: Stock change factors are in good agreement with the default values of the IPCC in general. For the tropical regions the assumptions changed notablly from the guidelines in 2006 to the update in 2019. leaving our results in very good agreement with the old default assumptions. Default assumption are given under the assumption of medium input systems, which, considering the yield gap in mainly developing regions in the tropics, might be an overestimation and decrease $F^{SOC}$ by additional 5-8 percent. Also: modelled $F^{SOC}$ have increased for all climates over time .")
# ```
# ```{r table, echo=FALSE}
# table <- readRDS("../ResultNotebooks/Output/SFC_climatezone.rds")
# knitr::kable(table$naturalstate_table[3:10,], "latex", digit=2, 
#              caption="S)
# ``` -->

@@
